%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Miha Zidar} % Your name
\address{\v{S}tihova ulica 25 \\ 1000 Ljubljana, Slovenia} % Your address
\address{+386~$\cdot$~40~$\cdot$~162~$\cdot$~722 \\ miha@zidar.me} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Specialized High School} \hfill {\em 2001 - 2006} \\ 
School of Electrical and Computer Engineering Ljubljana\\

{\bf Undergrad $+$ Masters} \hfill {\em 2006 - Present} \\ 
Faculty of Computer and Information Science \\


\begin{aSubsection}{Academic Focus}
\item Research in clowd computing and distributed storage
\item Research and implementation of data-mining algorithms
\item Research and development of kernel drivers for ARM embedded system
\item Development of general coursework assignments and exercises
\end{aSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Faculty of computer and information science}{Septemner2013 - ongoing}{Researcher}{Ljubljana, Slovenia}
\item Research of distributed file systems and cloud computing in the Laboratory for ubiquitous systems
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{AVG}{July 2012 - September 2012}{Intern}{San Francisco, California}
\item Developing browser extensions, and server side code to support the extension.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Double Recall}{June 2011 - August 2011}{Lead Developer}{Palo Alto, California}
\item Development of Double Recall Android development SDK and server side logic and API.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Double Recall}{February 2011 - June 2011}{Developer}{Ljubljana, Slovenia}
\item Developed the throttling control and security for both client and server side code.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Klik}{June 2009 - May 2011}{Developer}{Ljubljana, Slovenia}
\item Developed an in-house Store Management and Accounting Application using PHP and Javascript.
\item Implemented GIT version control for all projects.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Optika Clarus}{October 2006 - October 2007}{System Administrator and Developer}{Ljubljana, Slovenia}
\item Managed the computer system in an optical store chain to ensure smooth operation.
\item Developed smaller Delphi applications to increase efficiency and optimize resource usage.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Petrol}{June 2004 - December 2004}{System Administrator}{Ljubljana, Slovenia}
\item Replaced MS Windows servers with GNU Linux systems for the largest Slovenian petroleum company. Servers are still running well.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\newpage

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java, Android, Javascript, Python, PHP, Scala, Django, Bash, C, C++, \\
    Delphi & HTML, CSS \\
Protocols \& APIs & XML, JSON, SOAP, REST \\
Data storage & MySQL, PostgreSQL, Redis,  MongoDB \\
Tools & GIT, Vim, Android Studio, Eclipse, ADT, GNU Linux command line
\end{tabular}

\end{rSection}



%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\ \\

\begin{rSection}{}


\begin{aSubsection}{Achievements}
\item Member of Mensa Slovenia, since November 2013
\item JRS Data-mining Competition \hfill $1^{st}$ in the World
\item ACM International Collegiate Programming Contest \hfill Rep. of Slovenia
\item \#1 ComTrade Challenge \hfill $1^{st}$ in Nation
\item Slovenian National UPM Programming Competition \hfill $3^{rd}$ in Nation
\end{aSubsection}



\begin{aSubsection}{Journal Articles}
\item ``Team ULjubljana’s Solution to the JRS 2012 Data Mining Competition'' May 23. 2011: Co-author with Jure \v{Z}bontar, Marinka \v{Z}itnik, Gregor Majcen, Matic Poto\v{c}nik and Bla\v{z} Zupan
\item ``Reservoir Sampling Techniques in Modern Data Analysis'' March 15. 2011: Co-author with An\v{z}e Pe\v{c}ar and Matja\v{z} Kukar
\end{aSubsection}



\begin{aSubsection}{Other Interests}
\item I am an outgoing guy who enjoys surfing, skateboarding and drawing in my pastime. 
\item I am also fond of animals, and have done volunteer work at our local dog shelter as a trainer.
\end{aSubsection}





%Section content\ldots

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
